Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2022-01-25 edubots_surveys.Rnw
Totally deanonymized, now there are format errors
closes #78

Given the potential benefits that chatbots could bring to the classroom, the
focus of the
% EDUBOTS KA2 European project \footnote{https://www.edubots.eu},
{\sf anonymized European Project}, the sponsor of this study, is to
\textcolor{black}{explore best practices and innovative use of chatbots, and to create 
a learning community of educators in higher education institutions.
The majority of studies conducted so far have studied how these 
messaging applications and/or chatbots are used to deliver personalised
learning in classrooms that occurs anytime anywhere,
promote collaborative learning experiences, group discussions \cite{panah2020study}
and boost students' sense of belonging to their institutions
\cite{abbas2021onlinechat}. Hence, due to the paucity of research
that explores the use of these technologies from the teachers' perspectives,
this paper aims to investigate their opinions/needs and the
challenges/opportunities of adopting these technologies in classrooms
to paint a better picture of how they can positively contribute to enhancing
the learning process in higher education institutions.}

\textcolor{black}{In this study, data collection involved two phases:}
 \begin{itemize}
\item The first phase aimed to collect feedback from students about their actual
  needs \cite{MoraChatbots2021:anon}. Hence, the objective was to collect
  information about students’ preferences of tools/applications for chatting and
  messaging, how they use them in educational context, who do they like to be
  with in the class messaging groups, and their expectations of the chatbots in
  terms of assisting them during their learning process. Therefore, two surveys
  for bachelor and master degree students at the University of Granada (Spain)
  were designed and answers from more than 250 students were collected. The key
  findings of the students' surveys reveal that they prefer to use messaging
  applications, such as Telegram or WhatsApp as they are familiar to
  them. Students also expressed interest in chatbots that can assist them with
  organizing their course schedules, help them access their assignment grades
  and facilitate searching for course's resources.
\item The results of the first phase were fed into the second phase of the
  study, which focused on teachers’ opinions about using chatbots and messaging
  applications in classes. This is what is going to be presented in this paper.
\end{itemize}

@@

Along this line of research, our previous work \cite{MoraChatbots2021:anon}
aimed at analysing the expectations of students on this regard; recent papers
have also analysed how the use of chatbots affected the learning outcomes of
students in a Chinese class \cite{doi:10.1177/0735633120929622}. This paper
analysed conversational chatbots in an one-to-one setting, finding that learning
really benefited from it. This is, once again, a proof of the benefit of
chatbots in certain settings; however, there are some \textcolor{black}{prior experiences, as well as needs} that might
prevent the successful acceptance of the technology, and these are what we are
trying to find out in this paper, together with what kind of features would \textcolor{black}{improve
its acceptance}.

@@

\textcolor{black}{Comparing these results with those obtained in student surveys
in \cite{MoraChatbots2021:anon}, we have understood better} the differences between the teachers’
perspectives and/or intentions and that of their students when using the
messaging applications in higher education.  Teachers tend to adopt technologies
supported by their institutions.  This could be to ensure that their
universities can oversee their efforts in supporting their students during the
learning process.  Another reason could be their familiarity with the technology
provided by their institutions. On the other hand, students use the
non-institution messaging applications to form informal discussion groups with
their peers.  It is worth noting that peer support and collaboration is
inseparable from learning \cite{timmis2012constant} and correlates positively
with higher retention in higher education \cite{o2014front}.  Therefore, both
perspectives are complementary and play different roles in promoting the
learning process.

@@

% \section{Declarations}
% \label{sec:decl}
% 
% \subsection{Availability of data and materials}
% 
% The datasets generated and analysed during the current study are available in the {\tt edubots-paper} repository, accessible from https://anonymous.url
% % {\tt https://github.com/JJ/edubots-paper/tree/main/data}.
% 
% 
% \subsection{Competing interests}
% 
% The authors declare that they have no competing interests.
% 
% 
% \subsection{Funding}
% 
% This work has been supported by EDUBOTS project, funded under the scheme Erasmus + KA2: Cooperation for innovation and the exchange of good practices - Knowledge Alliances (grant agreement no: 612446).
% 
% \subsection{Authors' contributions}
% 
% All the authors have contributed to the study presented in this manuscript. (Rest hidden for double blind)
% 
% JJM has been the leader, drafted the first versions of the survey and supervised the writing of the manuscript.
% 
% PAC has revised the paper and researched the state of the art, as well as contributed to the survey design.
% AMM has revised the paper and researched the state of the art, as well as contributed to the survey design.
% FB has made the analysis and processed data and contributed to the survey design.
% NA has supervised the state of the art, and written the bulk of it, as well as contributed to discussion and conclusions.
% OT has performed data analysis, and contributed to discussion and conclusions.
% AG has contributed to the design of the survey, analysis, discussion and conclusions.
% 
% All authors have read and approved the final manuscript.
% 
% \subsection{Acknowledgements}
% 
% The authors want to thank to the educators who participated in the survey, and also people who have distributed the survey in their mailing lists, especially Mario García Valdez, Jesús Moreno León and the late José Raúl Canay.
% We would also like to thank the anonymous reviewers that have contributed greatly to the improvement of this paper.

>>>>

Given the potential benefits that chatbots could bring to the classroom, the
focus of the
EDUBOTS KA2 European project \footnote{https://www.edubots.eu},
the sponsor of this study, is to
\textcolor{black}{explore best practices and innovative use of chatbots, and to create 
a learning community of educators in higher education institutions.
The majority of studies conducted so far have studied how these 
messaging applications and/or chatbots are used to deliver personalised
learning in classrooms that occurs anytime anywhere,
promote collaborative learning experiences, group discussions \cite{panah2020study}
and boost students' sense of belonging to their institutions
\cite{abbas2021onlinechat}. Hence, due to the paucity of research
that explores the use of these technologies from the teachers' perspectives,
this paper aims to investigate their opinions/needs and the
challenges/opportunities of adopting these technologies in classrooms
to paint a better picture of how they can positively contribute to enhancing
the learning process in higher education institutions.}

\textcolor{black}{In this study, data collection involved two phases:}
 \begin{itemize}
\item The first phase aimed to collect feedback from students about their actual
  information about students’ preferences of tools/applications for chatting and
  messaging, how they use them in educational context, who do they like to be
  with in the class messaging groups, and their expectations of the chatbots in
  terms of assisting them during their learning process. Therefore, two surveys
  for bachelor and master degree students at the University of Granada (Spain)
  were designed and answers from more than 250 students were collected. The key
  findings of the students' surveys reveal that they prefer to use messaging
  applications, such as Telegram or WhatsApp as they are familiar to
  them. Students also expressed interest in chatbots that can assist them with
  organizing their course schedules, help them access their assignment grades
  and facilitate searching for course's resources.
\item The results of the first phase were fed into the second phase of the
  study, which focused on teachers’ opinions about using chatbots and messaging
  applications in classes. This is what is going to be presented in this paper.
\end{itemize}

@@

Along this line of research, our previous work \cite{MoraChatbots2021}
aimed at analysing the expectations of students on this regard; recent papers
have also analysed how the use of chatbots affected the learning outcomes of
students in a Chinese class \cite{doi:10.1177/0735633120929622}. This paper
analysed conversational chatbots in an one-to-one setting, finding that learning
really benefited from it. This is, once again, a proof of the benefit of
chatbots in certain settings; however, there are some \textcolor{black}{prior experiences, as well as needs} that might
prevent the successful acceptance of the technology, and these are what we are
trying to find out in this paper, together with what kind of features would \textcolor{black}{improve
its acceptance}.

@@

\textcolor{black}{Comparing these results with those obtained in student surveys
in \cite{MoraChatbots2021}, we have understood better} the differences between the teachers’
perspectives and/or intentions and that of their students when using the
messaging applications in higher education.  Teachers tend to adopt technologies
supported by their institutions.  This could be to ensure that their
universities can oversee their efforts in supporting their students during the
learning process.  Another reason could be their familiarity with the technology
provided by their institutions. On the other hand, students use the
non-institution messaging applications to form informal discussion groups with
their peers.  It is worth noting that peer support and collaboration is
inseparable from learning \cite{timmis2012constant} and correlates positively
with higher retention in higher education \cite{o2014front}.  Therefore, both
perspectives are complementary and play different roles in promoting the
learning process.

@@

\section{Declarations}
\label{sec:decl}

\subsection{Availability of data and materials}

The datasets generated and analysed during the current study are available in the {\tt edubots-paper} repository, accessible from https://anonymous.url
% {\tt https://github.com/JJ/edubots-paper/tree/main/data}.

\subsection{Competing interests}

The authors declare that they have no competing interests.

\subsection{Funding}

This work has been supported by EDUBOTS project, funded under the scheme Erasmus + KA2: Cooperation for innovation and the exchange of good practices - Knowledge Alliances (grant agreement no: 612446).

\subsection{Authors' contributions}

All the authors have contributed to the study presented in this manuscript. (Rest hidden for double blind)

JJM has been the leader, drafted the first versions of the survey and supervised the writing of the manuscript.

PAC has revised the paper and researched the state of the art, as well as contributed to the survey design.
AMM has revised the paper and researched the state of the art, as well as contributed to the survey design.
FB has made the analysis and processed data and contributed to the survey design.
NA has supervised the state of the art, and written the bulk of it, as well as contributed to discussion and conclusions.
OT has performed data analysis, and contributed to discussion and conclusions.
AG has contributed to the design of the survey, analysis, discussion and conclusions.

All authors have read and approved the final manuscript.

\subsection{Acknowledgements}

The authors want to thank to the educators who participated in the survey, and also people who have distributed the survey in their mailing lists, especially Mario García Valdez, Jesús Moreno León and the late José Raúl Canay.
We would also like to thank the anonymous reviewers that have contributed greatly to the improvement of this paper.
